Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2023-03-31 write-up/fda-recurrent.tex
Update fda-recurrent.tex

The goal of this paper is two-fold: (1) to discuss the appropriate choice of statistical model for joint high-frequency sensor data and the recurrent event data, and (2) to construct a simple, easy-to-implement method for parameter estimation and inference. For (1), we discuss an important issue regarding measurement-error models when paired with recurrent event outcomes. For (2), we introduce a random subsampling procedure that has several benefits.  First, the resulting inference is unbiased; however, there is a computation-efficiency trade-off. In particular, a higher sampling rate can decrease estimator variance at the cost of increased computation.  We show via simulations that the benefits of very high sampling rates is often negligible, as the contribution to the variation is small relative to the variation in the underlying stochastic processes. Second, derived estimating equations are optimal, implying loss of statistical efficiency is only due to subsampling procedure and not the derived methodology.  Finally, implementation can leverage existing, standard software for functional data analysis and logistic regression, leading to fast adoption by domain scientists.

@@

\begin{rmk}[Assessment of computational benefit]
Cool we have speed ups.
\end{rmk}

@@

\subsection{Selection of bandwidth} \label{section:bandwidth}

>>>>

The goal of this paper is to construct a simple, easy-to-implement method for parameter estimation and inference.
% For (1), we discuss an important issue regarding measurement-error models when paired with recurrent event outcomes.
To do so, we introduce a random subsampling procedure that has several benefits.  First, the resulting inference is unbiased; however, there is a computation-efficiency trade-off. In particular, a higher sampling rate can decrease estimator variance at the cost of increased computation.  We show via simulations that the benefits of very high sampling rates is often negligible, as the contribution to the variation is small relative to the variation in the underlying stochastic processes. Second, derived estimating equations are optimal, implying loss of statistical efficiency is only due to subsampling procedure and not the derived methodology.  Finally, implementation can leverage existing, standard software for functional data analysis and logistic regression, leading to fast adoption by domain scientists.

@@

% \begin{rmk}[Assessment of computational benefit]
% Cool we have speed ups.
% \end{rmk}

@@

\begin{newmaterial}
\subsection{Selection of bandwidth} \label{section:bandwidth}
